\huge ARuko and Editour: \\ \Large A Platform for Augmented Reality Tour Guide Apps

### 2019-10-03 paper.tex
added section on scrapped ar use cases

>>>>

\subsection{Alterniative Uses for AR in ARuko}
\label{sec:alternativeARukoAR}

Even once the idea for ARuko was settled on audio tour functionality with 
additional AR components, what exactly those AR components would do was still
undecided for a while. Atticus knew he wanted to use AR on the tour, but wasn't
sure what to do with it. At first, we made recommendations to him based on the
capabilities of Vuforia that we found in our research. We knew it was good at
image recognition and ground plane recognition, so we suggested that maybe 
displaying some sorts of 3D models in certain locations using either of these
features might be an interesting way to expand on the tour. With these 
recommendations in mind, Atticus expressed interest in the capability of using
building facades as image targets. The intention then would be to tie content
related to a specific location within Kinkaku-ji to that physical location, and
use images of the location as targets. As previously explained, this ultimately
did not work out due to the limitations of image recognition with Vuforia.

After being initially deterred from image recognition, we thought that ground
and mid-air plane recognition might the best way to implement AR in the app. 
It didn't have to rely on images that meet Vuforia's criteria, and since it 
could be triggered anywhere, it seemed like a good fit for an app focusing on
walking around a site. Atticus explained that he primarily wanted to use AR to
display art related to the site. So we focused our efforts with ground and 
mid-air plane AR on ways to display 2D images. What we ended up creating first
was a feature that allowed you to view certain images in AR, using ground plane
detection, based on what region you were in. So when you entered a region of 
the tour, the image menu would be dynamically populated with buttons that, when
tapped, would create a Plane primitive in Unity with the given image displayed
on it and place it on the ground plane.

We encountered a few notable problems with this though. One problem was that 
the Plane we made was always the same size and dimensions, and would cause 
images to stretch to fit the plane. Further testing to change the size of the
plane with each picture proved difficult. Additionally, using a Plane primitive
had problematic effects on the way the object was lit in the Unity scene, as 
well as how it appeared when not viewed head-on. If viewed from an angle, the 
picture could become very dark and difficult to see. And if viewed from behind,
it would actually be completely invisible. Because of these issues, we decided
to place the images on a 3D Cube primitive instead. But after showing this
feature to Atticus during early testing at Kinkaku-ji, he decided that he 
wanted to move away from displaying images in AR. Looking back, the feature
may have worked better with mid-air plane recognition so that the user could
place the image directly in front of them.

In addition to the previously mentioned use cases for AR in ARuko, Atticus also
expressed interest in using AR to trigger video content. He was particularly
interested in 3D videos triggerable through AR. As the scope of the project 
grew, and time ran short, the task of including 3D videos triggered by AR 
seemed more and more complicated, causing that idea to be phased out of the
final project. Additionally, we never received any assets from Atticus to use
for this feature, thus preventing us from spending time developing it.
